### 2020-07-01 README.Rmd
update README

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

@@

``` r
# install.packages("devtools")
devtools::install_github("antaldaniel/eurobarometer")
```
## Workflow

Not all elements of the [Workflow](http://eurobarometer.danielantal.eu/articles/workflow.html) are implemented yet.

@@

The SPSS files in GESIS are not ready for programmatic use in R, because the variable names often contain reserved special characters. You should use `gesis_metadata_create()` to understand what are the possible problems in the SPSS file and how to resolve them. (See: [Working With Metadata](http://eurobarometer.danielantal.eu/articles/metadata.html))

* The naming functions `normalize_names()` removes regex symbols, whitespace, and basic inconsistencies in abbreviations. The function `canonical_names()`harmonizes the names across various GESIS files, so that they can be joined into panels across time.

* You can read in the SPSS file to R in [haven](https://haven.tidyverse.org/), which will result in many `labelled` variables. The metadata file contains a suggestion of the most practical class conversion for data analysis. You can review and change this suggestion and then make the conversions at once with `convert_class()`

See `vignette("metadata")`

@@

* Currently `code_nuts1()` and `code_nuts2()` is implemented but this will be replaced with a more comprehensive `NUTS0`-`NUTS3` level helper function to make the regional coding consistent.

>>>>

```{r, include = FALSE}
figures_rel_path_from_root <- rprojroot::find_root_file(
  "man", "figures", "README", 
  criterion = rprojroot::has_file("DESCRIPTION"))

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = figures_rel_path_from_root,
  out.width = "100%"
)
```

@@

``` r
# install.packages("devtools")
devtools::install_github("antaldaniel/eurobarometer")
```

@@

The SPSS files in GESIS are not ready for programmatic use in R or for joining into longitudinal panels.

1. We import the GESIS SPSS files with the help of the [haven](https://haven.tidyverse.org/) package. In order to preserve the metadata in the files (particularly variable- and value labels, and user-defined missing values) these are converted to labelled classes.

2. We analyse the files with `gesis_metadata_create()` to understand what are the possible problems in the SPSS file and how to resolve them. (See: [Working With Metadata](http://eurobarometer.danielantal.eu/articles/metadata.html) or `vignette("metadata")`)

3. We suggest various [naming](http://eurobarometer.danielantal.eu/articles/variable_names.html) and [harmonization](http://eurobarometer.danielantal.eu/articles/workflow.html) changes in the data as a data processing step. These suggested changes can be modified by the user.

4. We convert the variables to a modified version of the `haven_labelled_spss` class that contains the harmonized values, harmonized labels, harmonized missing values codes of the variable with their history (original values, labels, and function applied to change them)  for reproducibility. The [eurobarometer_labelled](http://eurobarometer.danielantal.eu/articles/eurobarometer_class.html) class inherits most of the functionality of the packages [haven](https://haven.tidyverse.org/),  [labelled](https://cran.r-project.org/web/packages/labelled/vignettes/intro_labelled.html) and are expected to work well with [sjlabelled](https://strengejacke.github.io/sjlabelled/articles/labelleddata.html).

```{r, echo=FALSE, fig.align='center', out.width='90%', fig.cap="Workflow from 'Introduction to labelled by Joseph Larmaranged'"}
knitr::include_graphics(file.path(figures_rel_path_from_root, 
                                  'labelled_workflow.png'))
```

Our approach follows `Approach B` to allow the conversion of harmonized and joined files back into SPSS.

5. The [eurobarometer_labelled](http://eurobarometer.danielantal.eu/articles/eurobarometer_class.html) class comes with simple methods that can convert all variables to the base R types of numeric or factor, and they are ready to be used with any R statistical packages and tidyverse data processing tools. Alternatively, they can be exported back to [SPSS](https://haven.tidyverse.org/reference/read_spss.html) or [Stata](https://haven.tidyverse.org/reference/read_dta.html) files with the functions of the [haven](https://haven.tidyverse.org/) package.

@@
